NEED TITLE

### 2014-12-23 ms.tex
Added Average.pdf files, caption, and discussion

At the instance in time shown in Figure \ref{fig:entire projection}, a total of five star particles have been formed.  However, these star particles are not formed in isolation.  Rather they congregate in two star forming regions shown in Figure \ref{fig:star forming regions}.  In these regions, the sink particles that are formed lay within 0.1 pc of one another, which reflects that the highest density regions are concentrated toward the center.  Visually, the character of accretion at the this outer scale appear to flow along filaments, thought previous work (Lee et al. 2014) has shown that the majority of accretion is spherical.  We discuss this more quantitatively below {\bf INCLUDE A STUDY OF LARGE SCALE ACCRETION}

@@

{\bf INCLUDE ACCRETION TOPOLOGY STUDY HERE.}

>>>>

At the instance in time shown in Figure \ref{fig:entire projection}, a total of five star particles have been formed.  However, these star particles are not formed in isolation.  Rather they congregate in two star forming regions shown in Figure \ref{fig:star forming regions}.  In these regions, the sink particles that are formed lay within 0.1 pc of one another, which reflects that the highest density regions are concentrated toward the center.  Visually, the character of accretion at the this outer scale appear to flow along filaments, though previous work (Lee et al. 2014) has shown that the majority of accretion is spherical.  We discuss this more quantitatively below {\bf INCLUDE A STUDY OF LARGE SCALE ACCRETION}

@@

\begin{figure*}
\plottwo{Average_5_013.pdf}{Average_5_24.pdf}
\plottwo{Average_02_013.pdf}{Average_02_24.pdf}
\caption{Here we show the mass accretion rates as a function of density.  The upper figures are displaying rates corresponding to a region of $0.5$ pc around the particle, while the lower figures are showing a radius of $0.02$ pc.  The two plots on the left show the region with three particles forming, and the plots on the right show the region with two particles forming.  The more massive region with three particles indicates the mass is coming in at a density value roughly three times the average density, and the curves are similar between the smaller and larger radii.  The graph for the less massive region on the right shows a distinctly separate profile between the larger and the smaller radius.   \label{fig:accretion average rho}}
\end{figure*}

In prior work, we examined the geometry of accretion, i.e., does the accretion proceed along filament or over 4$\pi$ steradian, by plotting the cumulative accretion rate as a function of density. In Figure \ref{fig:accretion average rho}, we plot the cumulative accretion rate as a function of density, normalized to the average density in shells of radii 0.5 (upper plots) and 0.02 pc (lower plots).  Plots on the left are associated with the more massive star forming region, where 3 star particles reside and plots on the right are associated with the less massive star forming region, where two star particles reside.  The density where 50\% of the accretion is accounted for occurs at $\rho/\bar{\rho} \approx 3$ for the more massive star forming region and appears to be independent of whether the shell has a radius of 0.5 or 0.02 pc.  On the other hand, the less massive star forming region has half of the accretion account for at $\rho/\bar{\rho} \approx 10$ at r=0.5 pc.  This suggests that the accretion is directed along filaments.  This filamentary nature of accretion does not maintain itself to lower radii, where at 0.02 pc, the 50\% point in cumulatiove accertion occurs at $\rho/\bar{\rho} \approx 1$, which suggest accretion along $4\pi$ steradian.
{\bf INCLUDE ACCRETION TOPOLOGY STUDY HERE.}
